\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities

### 2019-07-30 manuscript/appendices.tex
revision

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

@@

% Frontmatter
\title{\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities}
\date{November 5, 2018}
%\author{Nils Karl Reimer}
%\author[2]{Shanmukh V. Kamble}
%\author[3]{Katharina Schmid}
%\author[1]{Miles Hewstone}
%\affil[1]{University of Oxford}
%\affil[2]{Karnatak University}
%\affil[3]{ESEADE Business School, Ramon Llull University}
%\renewcommand\Affilfont{\small}

@@

\section{Appendix B: Social Identity Structures}

Van Dommelen et al. \citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e. the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e. the specific structures proposed by \citeA{roccas_social_2002}. Neither measure translated well to the present study. As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample. Coding structures was interesting in principle, but proved difficult in practice.  Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''. Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:b-1}). The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
\small	
\begin{tabular}{rlrrrr|rr} \toprule
\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
\end{tabular}
\label{tab:b-1}
\end{table}

Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances. We operationalised \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure. Figure~\ref{fig:b-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses. Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure. Numbers (on the right) show the median edit distance per structure. %Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
}
\label{fig:b-1}
\end{figure}

@@

\section{Appendix C: Intergroup Threat}

@@

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Model comparison for intergroup threat]{Comparison of models estimating participants' intergroup threat. We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
\# &  &  Description &  $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
0 &      & \textit{Varying intercept} & .31 & -3368.1 & 32.9 & - & - & - & .11 \\
1 & vs 0 & \textit{Subscales}         & .31 & -3368.9 & 32.9 & -0.8 & 0.6 & -1.3 & .00 \\
2 & vs 0 & \textit{Outgroups} & .32 & -3363.7 & 33.0 & 4.4 & 3.3 & 1.3 & .00 \\
3 & vs 0 & \textit{Subscales $\times$ Outgroups} & .33 & -3335.1 & 34.0 & 33.0 & 8.4 & 3.9 & .19 \\ \midrule
4 & vs 3 & \textit{Categorizations}   & .33 & -3335.5 & 34.0 & -0.3 & 0.6 & -0.5 & .00 \\
5 & vs 3 & \textit{Categorizations}   & .34 & -3330.5 & 34.0 & 4.7 & 3.6 & 1.3 & .71 \\
6 & vs 3 & \textit{Categorizations}   & .33 & -3336.7 & 34.0 & -1.5 & 0.7 & -2.1 & .00 \\
7 & vs 3 & \textit{Categorizations}   & .34 & -3332.8 & 34.0 & 2.3 & 3.6 & 0.6 & .00 \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:c-1}
\end{table}

Model~3, but not Models 1 and 2, improved upon the predictions of Model~0 (Table~\ref{tab:c-1}), showing that participants' perceptions of symbolic and realistic threat depended on whether the relevant outgroup was Muslims or Dalits. Specifically, participants reported more realistic ($ \beta_1 = 3.62$, $[3.49, 3.75]$) than symbolic ($\beta_2 = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, $\text{Pr} (\beta_1 > \beta_2|M3) > .99$, but less realistic ($\beta_3 = 3.23$, $[3.06, 3.38]$) than symbolic ($\beta_4 = 3.47$, $[3.34, 3.61]$) threat from (different-religion) Muslims, $\text{Pr} (\beta_3 < \beta_4| M3) > .99$.

@@

\section{Appendix D: Support for Social Change}

We tested whether more inclusive identities increase support for affirmative action among advantaged-group members, but decrease support for these policies among disadvantaged-group members. First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantages and in their support for affirmative action. Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses. We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change). We examined participants' responses to measures concerning their ingroup to test the \emph{demobilisation hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilisation hypothesis} (that negative contact encourages disadvantaged-group members to support social change).

@@

Figure \ref{fig:d-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1. For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other. On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed. General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background. General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds. Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds. General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''. Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'. For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average. General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint. Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-7}
\caption{
Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:d-1}
\end{figure}

Figure \ref{fig:d-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1. General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity. General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$). Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students. Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$). Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-8}
\caption{
Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:d-2}
\end{figure}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
\small	
\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:d-1}
\end{table}

>>>>

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{subcaption}

@@

% Frontmatter
\title{\emph{Appendices for}\\Intergroup contact fosters\\more inclusive social identities}
\date{July 30, 2019}

@@

\section{Appendix B: Descriptive Statistics}

Table~\ref{tab:b-1} reports means and standard deviations for all variables. Tables~\ref{tab:b-2} to \ref{tab:b-5} report correlations between all variables for various ingroups and outgroups.

\begin{table}[!hp]
\centering
\figureversion{lining, tabular}
\caption{Means and standard deviations (in brackets) for all measured combinations of outgroups (rows) and ingroups (columns).}
\small	
\begin{tabular}{llrrr} \toprule
Variable & Outgroup & GM & OBC & SC/ST \\ \midrule \addlinespace
  Contact quantity & GM & - & 4.21 (0.96) & 3.84 (1.02) \\ 
  Contact quantity & OBC & 3.74 (1.12) & - & 4.04 (0.94) \\ 
  Contact quantity & SC/ST & 3.76 (1.10) & 3.92 (0.98) & - \\ 
  Contact quantity & Muslims & 3.49 (1.30) & 3.54 (1.17) & 3.49 (1.19) \\ \addlinespace
  Positive contact & GM & - & 4.03 (1.01) & 3.91 (1.05) \\ 
  Positive contact & OBC & 3.83 (1.01) & - & 3.84 (1.13) \\ 
  Positive contact & SC/ST & 3.68 (0.98) & 3.70 (1.19) & - \\ 
  Positive contact & Muslims & 3.40 (1.21) & 3.64 (1.13) & 3.53 (1.29) \\ \addlinespace
  Negative contact & GM & - & 2.17 (1.30) & 2.27 (1.30) \\ 
  Negative contact & OBC & 1.96 (1.19) & - & 2.38 (1.32) \\ 
  Negative contact & SC/ST & 1.99 (1.13) & 1.88 (1.13) & - \\ 
  Negative contact & Muslims & 2.44 (1.30) & 2.20 (1.20) & 2.28 (1.23) \\ \addlinespace
  Friendship & GM & - & 4.21 (0.84) & 3.95 (0.85) \\ 
  Friendship & OBC & 3.58 (1.00) & - & 4.03 (0.85) \\ 
  Friendship & SC/ST & 3.43 (0.96) & 3.66 (1.00) & - \\ 
  Friendship & Muslims & 3.20 (1.12) & 3.37 (0.95) & 3.30 (0.93) \\ \addlinespace
  (Dis-)advantage & GM & 2.83 (2.13) & 2.86 (2.02) & 4.08 (1.96) \\ 
  (Dis-)advantage & OBC & 4.89 (1.68) & 3.90 (1.81) & 4.11 (1.70) \\ 
  (Dis-)advantage & SC/ST & 5.44 (1.65) & 5.40 (1.79) & 4.30 (2.01) \\ 
  (Dis-)advantage & Muslims & 4.26 (1.83) & 4.34 (1.77) & 3.84 (1.96) \\ \addlinespace
  Policy support & OBC & 2.66 (1.35) & 3.79 (1.03) & 3.54 (0.94) \\ 
  Policy support & SC/ST & 1.91 (1.15) & 2.28 (1.18) & 4.22 (0.88) \\ 
  Policy support & Muslims & 2.62 (1.23) & 2.82 (1.17) & 3.28 (1.30) \\ \addlinespace
  Realistic threat & SC/ST & 3.79 (1.16) & 3.48 (1.06) & - \\ 
  Realistic threat & Muslims & 3.39 (1.09) & 3.06 (1.00) & 3.24 (1.10) \\ \addlinespace
  Symbolic threat & SC/ST & 3.28 (1.07) & 3.18 (1.06) & - \\ 
  Symbolic threat & Muslims & 3.60 (1.17) & 3.37 (1.12) & 3.53 (1.27) \\ \addlinespace
  SDO-D &  & 0.02 (0.71) & -0.04 (0.74) & 0.05 (0.78) \\ 
  SDO-E &  & 0.14 (0.72) & -0.06 (0.68) & -0.07 (0.82) \\  \bottomrule
\end{tabular}
\label{tab:b-1}
\end{table}

\begin{table}[!hp]
\centering
\figureversion{lining, tabular}
\caption{Correlations between variables for GM (above the diagonal) and SC/ST (below the diagonal) participants with people from other backward classes (OBCs) as the relevant outgroup.}
\small	
\begin{tabular}{rlrrrrrrrr} \toprule
\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 \\ \midrule 
1 & Contact quantity &  &  .63 &  .01 &  .67 &  .22 & -.12 & -.06 & -.02 \\ 
  2 & Positive contact &  &  & -.12 &  .55 &  .04 &  .02 & -.08 & -.03 \\ 
  3 & Negative contact & -.28 &  &  &  .01 &  .01 &  .11 &  .13 &  .10 \\ 
  4 & Friendship &  .41 &  .49 &  &  &  .16 & -.06 & -.10 & -.06 \\ 
  5 & (Dis-)advantage &  .14 &  .12 & -.05 &  &  & -.22 & -.09 & -.03 \\ 
  6 & Policy support &  .11 &  .12 & -.19 &  .13 &  &  &  .14 &  .15 \\ 
  7 & SDO-D &  .11 &  .06 &  .15 &  .13 &  .14 &  &  &  .43 \\ 
  8 & SDO-E & -.05 &  .17 & -.03 &  .03 &  .14 &  .15 &  &  \\ 
\bottomrule
\end{tabular}
\label{tab:b-2}
\end{table}

\begin{table}[!hp]
\centering
\figureversion{lining, tabular}
\caption{Correlations between variables for OBC (above the diagonal) and SC/ST (below the diagonal) participants with people from general castes (GM) as the relevant outgroup.}
\small	
\begin{tabular}{rlrrrrrrr} \toprule
\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7  \\ \midrule 
1 & Contact quantity &  &  .64 & -.31 &  .60 & -.00 & -.10 & -.03 \\ 
  2 & Positive contact &  &  & -.27 &  .63 & -.12 & -.07 & -.11 \\ 
  3 & Negative contact & -.03 &  &  & -.27 & -.04 &  .00 & -.05 \\ 
  4 & Friendship &  .17 &  .42 &  &  & -.07 & -.08 & -.12 \\ 
  5 & (Dis-)advantage &  .06 & -.02 & -.04 &  &  &  .09 &  .01 \\ 
  6 & SDO-D &  .15 &  .08 &  .14 &  .14 &  &  &  .46 \\ 
  7 & SDO-E &  .06 & -.02 &  .15 & -.06 &  .10 &  &  \\  
\bottomrule
\end{tabular}
\label{tab:b-3}
\end{table}

\newpage

\begin{table}[!hp]
\centering
\figureversion{lining, tabular}
\caption{Correlations between variables for GM (above the diagonal) and OBC (below the diagonal) participants with Dalits (SC/ST) as the relevant outgroup.}
\small	
\begin{tabularx}{\linewidth}{r@{~~}X@{~~}rrrrrrrrrr} \toprule
\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \midrule 
1 & Contact quantity &  &  .47 & -.14 &  .41 &  .28 & -.20 &  .25 &  .09 & -.03 & -.06 \\ 
  2 & Positive contact &  &  & -.30 &  .18 &  .31 &  .02 & -.08 & -.08 & -.03 & -.09 \\ 
  3 & Negative contact &  .05 &  &  & -.01 & -.15 &  .03 &  .16 &  .22 &  .13 & -.10 \\ 
  4 & Friendship &  .31 &  .40 &  &  &  .06 & -.10 &  .07 & -.05 & -.12 & -.10 \\ 
  5 & (Dis-)advantage & -.03 & -.02 & -.23 &  &  & -.21 &  .24 & -.06 &  .06 &  .14 \\ 
  6 & Policy support &  .13 &  .21 &  .12 & -.03 &  &  & -.33 &  .06 &  .30 &  .04 \\ 
  7 & Realistic threat &  .04 &  .10 &  .03 & -.03 &  .08 &  &  &  .39 & -.03 &  .02 \\ 
  8 & Symbolic threat & -.12 &  .02 &  .16 & -.08 & -.04 & -.05 &  &  &  .35 & -.03 \\ 
  9 & SDO-D & -.11 &  .01 &  .18 &  .09 &  .11 &  .07 &  .14 &  &  &  .43 \\ 
  10 & SDO-E & -.08 &  .11 &  .02 &  .04 &  .13 &  .15 &  .13 &  .10 &  &  \\ 
\bottomrule
\end{tabularx}
\label{tab:b-4}
\end{table}

\begin{table}[!hp]
\centering
\figureversion{lining, tabular}
\caption{Correlations between variables for all non-Muslims participants with Muslims as the relevant outgroup.}
\small	
\begin{tabularx}{\linewidth}{r@{~~}X@{~~}rrrrrrrrrr} \toprule
\# & Variable & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \midrule 
1 & Contact quantity &  &  .64 & -.11 &  .61 &  .17 &  .10 & -.11 & -.18 & -.04 & -.01 \\ 
  2 & Positive contact &  .64 &  & -.18 &  .65 &  .14 &  .15 & -.19 & -.22 & -.04 & -.06 \\ 
  3 & Negative contact & -.11 & -.18 &  & -.12 & -.01 & -.08 &  .14 &  .22 &  .17 &  .02 \\ 
  4 & Friendship &  .61 &  .65 & -.12 &  &  .03 &  .11 & -.21 & -.25 &  .01 & -.03 \\ 
  5 & (Dis-)advantage &  .17 &  .14 & -.01 &  .03 &  & -.16 &  .11 &  .06 &  .02 &  .00 \\ 
  6 & Policy support &  .10 &  .15 & -.08 &  .11 & -.16 &  & -.17 & -.14 &  .05 & -.01 \\ 
  7 & Realistic threat & -.11 & -.19 &  .14 & -.21 &  .11 & -.17 &  &  .51 &  .10 &  .08 \\ 
  8 & Symbolic threat & -.18 & -.22 &  .22 & -.25 &  .06 & -.14 &  .51 &  &  .13 &  .07 \\ 
  9 & SDO-D & -.04 & -.04 &  .17 &  .01 &  .02 &  .05 &  .10 &  .13 &  &  .46 \\ 
  10 & SDO-E & -.01 & -.06 &  .02 & -.03 &  .00 & -.01 &  .08 &  .07 &  .46 &  \\ 
\bottomrule
\end{tabularx}
\label{tab:b-5}
\end{table}

\newpage

\section{Appendix C: Social Identity Structures}

Van Dommelen et al. \citeyear{dommelen_construing_2015} analysed participants' responses as \emph{Social Identity Inclusiveness}, i.e. the total number of 24 targets a participant had categorized as ``us'', and as \emph{Social Identity Structures}, i.e. the specific structures proposed by \citeA{roccas_social_2002}. Neither measure translated well to the present study. As participants had different caste backgrounds, comparing their inclusiveness scores ($M = 15.34$, $\textit{SD} = 4.88$, $\textit{Mdn} = 16$) was less meaningful than in \citeauthor{dommelen_construing_2015}'s sample. Coding structures was interesting in principle, but proved difficult in practice.  Few (9\%, $n = 26$) participants consistently classified all targets in each category as either ``us'' or ``not us''. Relatedly, how participants classified targets within a category was correlated, but only moderately so ($.41 \leq rs \leq.66$, see Table ~\ref{tab:c-1}). The inconsistency in participants' responses made hard and fast coding rules, as used by \citeauthor{dommelen_construing_2015}, impractical.

Instead, we quantified the (dis)similarity between a participant's responses and various proposed social identity structures by calculating edit distances. We operationalized \emph{edit distance} as the number of a participant's categorizations that would need to change from ``us'' to ``not us'' (and vice versa) to make them identical to the categorizations implied by a certain structure. Figure~\ref{fig:c-1} shows the distributions of participants' edit distances from each structure, as well as median edit distances.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/appendices/appendices-b-1}
\caption[Edit distances between social identity structures and participants' responses]{Edit distances between each social identity structure and participants' responses. Edit distance is the sum of all categorizations in which a participant's responses differed from the ones implied by the proposed structure. Numbers (on the right) show the median edit distance per structure. %Points indicate the median \emph{social identity inclusiveness} of participants' responses at a specific edit distance.
}
\label{fig:c-1}
\end{figure}

@@

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Mean intra and inter-category correlations for target categorizations]{Mean \emph{intra}-category (\textbf{diagonal}) and \emph{inter}-category correlations between participants' categorizations of targets in the respective categories.}
\small	
\begin{tabular}{rlrrrr|rr} \toprule
\# & Category            & 1   & 2   & 3   & 4   & 5   & 6   \\ \midrule \addlinespace
1  & Indian, Hindu, GM   & \textbf{.48} & .56 & .33 & .43 & .16 & .08 \\
2  & Indian, Hindu, OBC  & .56 & \textbf{.41} & .29 & .46 & .09 & .06 \\
3  & Indian, Hindu, SCST & .33 & .29 & \textbf{.66} & .35 & .03 & .16 \\
4  & Indian, Muslim, OBC & .43 & .46 & .35 & \textbf{.52} & .01 & .24 \\ \midrule
5  & Foreign, Hindu      & .16 & .09 & .03 & .01 & \textbf{.50} & .47 \\
6  & Foreign, Muslim     & .08 & .06 & .16 & .24 & .47 & \textbf{.51} \\ \addlinespace \bottomrule
\end{tabular}
\label{tab:c-1}
\end{table}

\section{Appendix D: Intergroup Threat}

@@

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Model comparison for intergroup threat]{Comparison of models estimating participants' intergroup threat. We preferred a more complex model over a simpler model when $\frac{\Delta\textit{ELPD}}{\textit{SE}} \geq 2$.}
\small	
\begin{tabularx}{\linewidth}{r@{~}rXrrrrrrr} \toprule
\# &  &  Description &  $R^2$ & $\textit{ELPD}$ & $\textit{SE}$ & $\Delta\textit{ELPD}$ & $\textit{SE}$ & $\frac{\Delta\textit{ELPD}}{\textit{SE}}$ & $w$ \\ \midrule \addlinespace
0 &      & \textit{Varying intercept} & .31 & -3368.1 & 32.9 & - & - & - & .11 \\
1 & vs 0 & \textit{Subscales}         & .31 & -3368.9 & 32.9 & -0.8 & 0.6 & -1.3 & .00 \\
2 & vs 0 & \textit{Outgroups} & .32 & -3363.7 & 33.0 & 4.4 & 3.3 & 1.3 & .00 \\
3 & vs 0 & \textit{Subscales $\times$ Outgroups} & .33 & -3335.1 & 34.0 & 33.0 & 8.4 & 3.9 & .19 \\ \midrule
4 & vs 3 & \textit{Categorizations}   & .33 & -3335.5 & 34.0 & -0.3 & 0.6 & -0.5 & .00 \\
5 & vs 3 & \textit{Categorizations}   & .34 & -3330.5 & 34.0 & 4.7 & 3.6 & 1.3 & .71 \\
6 & vs 3 & \textit{Categorizations}   & .33 & -3336.7 & 34.0 & -1.5 & 0.7 & -2.1 & .00 \\
7 & vs 3 & \textit{Categorizations}   & .34 & -3332.8 & 34.0 & 2.3 & 3.6 & 0.6 & .00 \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:d-1}
\end{table}

Model~3, but not Models 1 and 2, improved upon the predictions of Model~0 (Table~\ref{tab:d-1}), showing that participants' perceptions of symbolic and realistic threat depended on whether the relevant outgroup was Muslims or Dalits. Specifically, participants reported more realistic ($ \beta_1 = 3.62$, $[3.49, 3.75]$) than symbolic ($\beta_2 = 3.21$, $[3.09, 3.33]$) threat from (same-religion) Dalits, $\text{Pr} (\beta_1 > \beta_2|M3) > .99$, but less realistic ($\beta_3 = 3.23$, $[3.06, 3.38]$) than symbolic ($\beta_4 = 3.47$, $[3.34, 3.61]$) threat from (different-religion) Muslims, $\text{Pr} (\beta_3 < \beta_4| M3) > .99$.

@@

\section{Appendix E: Support for Social Change}

We tested whether more inclusive identities increase support for affirmative action among advantaged-group members, but decrease support for these policies among disadvantaged-group members. First, we tested for \emph{group differences} in participants' perceptions of (dis-)advantages and in their support for affirmative action. Second, we analysed to what extent contact experiences and ingroup construals explained \emph{individual differences} in participants' responses. We examined participants' responses to measures concerning outgroup members to test the \emph{solidarity hypothesis} (that positive contact encourages advantaged-group members to support social change). We examined participants' responses to measures concerning their ingroup to test the \emph{demobilization hypothesis} (that positive contact discourages disadvantaged-group members from supporting social change) and the \emph{mobilization hypothesis} (that negative contact encourages disadvantaged-group members to support social change).

@@

Figure \ref{fig:e-1} shows estimated mean ratings of perceived (dis-)advantage for all target groups as a function of participants' caste memberships in Model~1. For most target groups, General Merit and Other Backward Class participants' responses closely resembled each other. On average, General Merit~/ Other Backward Class participants thought that it was somewhat hard (below the midpoint) for ``people from [their] own background'' to succeed. General Merit~/ Other Backward Class participants agreed with each other that it was a lot easier for people from Scheduled Caste~/ Scheduled Tribe backgrounds to succeed, compared to people from their own background. General Merit~/ Other Backward Class participants also agreed that, of all target groups, life was most difficult for people from General Merit backgrounds. Other Backward Class participants disagreed with General Merit participants when rating life difficulty for people from Other Backward Class backgrounds. General Merit participants rated life difficulty for Other Backward Class people as somewhat easy, while Other Backward Class participants tended toward ``neither easy nor hard'' and ``somewhat hard''. Scheduled Caste~/ Scheduled Tribe participants' responses differed markedly from General Merit and Other Backward Class participants'. For all target groups, Scheduled Caste~/ Scheduled Tribe participants rated life difficulty as ``neither easy nor hard'', on average. General Merit, Other Backward Class, and Scheduled Caste~/ Scheduled Tribe participants all tended to rate life difficulty for Muslims as around the midpoint. Overall, participants' responses seemed to contradict, or even reverse, persisting social inequalities.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-7}
\caption{
Posterior probabilities of perceived (dis-)advantage ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:e-1}
\end{figure}

Figure \ref{fig:e-2} shows estimated policy support---that is, support for reservations benefiting Scheduled Caste~/ Scheduled Tribe, Other Backward Class, and Muslim students---as a function of participants' caste memberships in Model~1. General Merit and Other Backward Class participants' responses did not provide evidence for cross-group solidarity. General Merit participants tended to oppose reservations for Scheduled Caste~/ Scheduled Tribe ($M = 1.87$, $[1.63, 2.12]$), Other Backward Class ($M = 2.70$, $[2.44, 2.96]$), and Muslim students ($M = 2.75$, $[2.46, 3.01]$). Other Backward Class participants tended to support reservations for their own group ($M = 3.72$, $[3.50, 3.95]$), but not for Scheduled Caste~/ Scheduled Tribe ($M = 2.31$, $[2.10, 2.53]$) or Muslim ($M = 2.79$, $[2.55, 3.04]$) students. Scheduled Caste~/ Scheduled Tribe participants tended to support reservations for their own group ($M = 4.16$, $[3.88, 4.45]$), for Other Backward Class students ($M = 3.57$, $[3.27, 3.86]$), and, to a lesser extent, for Muslim students ($M = 3.24$, $[2.92, 3.57]$). Overall, participants' responses provided evidence for solidarity from Scheduled Caste~/ Scheduled Tribe participants to Other Backward Class students, but not for solidarity from General Merit and Other Backward Class participants to Scheduled Caste~/ Scheduled Tribe students.

\begin{figure}
\centering
\includegraphics[scale=1]{../figures/figure-8}
\caption{
Posterior probabilities of policy support ratings for different target groups (right) by participants' caste ingroup (left). Diamonds mark the most plausible estimate of each mean rating; intervals encompass the 97\% most plausible estimates. GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe.
}
\label{fig:e-2}
\end{figure}

\begin{table}
\centering
\figureversion{lining, tabular}
\caption[Estimated residual correlations in Models 0 and 1 for Study 4]{Estimated residual correlations between six \emph{perceived life difficulty} (PD) ratings and three \emph{policy support} (PS) ratings in Model~0 (below the diagonal) and Model~1 (above the diagonal) for Study 4.}
\small	
\begin{tabularx}{\linewidth}{rl@{~}Xrrrrrr|rrr} \toprule
\# & \multicolumn{2}{l}{Variable} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 \\ \midrule \addlinespace
1 & PD, & \ldots own background & \textbf{}  & .14 & .30 & .45 & .43 & .05 & .28 & .12 & .14 \\
2 & PD, & SC/ST  & .10 & \textbf{} & .33 & -.13 & -.09 & .28 & -.12 & -.10 & -.05 \\
3 & PD, & OBC    & .28 & .33 & \textbf{} & .20 & .16 & .32 & .05 & -.17 & -.13  \\
4 & PD, & GM     & .47 & -.18 & .18 & \textbf{} & .61 & -.08 & .24 & .15 & .02 \\
5 & PD, & Hindu  & .44 & -.12 & .15 & .62 & \textbf{} & -.01 & .29 & .11 & .03  \\
6 & PD, & Muslim & .04 & .28 & .31 & -.10 & -.02 & \textbf{} & .02 & -.17 & -.15 \\ \midrule
7 & PS, & SC/ST  & .29 & -.24 & -.03 & .33 & .30 & -.03 & \textbf{} & .24 & .34 \\
8 & PS, & OBC    & .11 & -.13 & -.25 & .17 & .12 & -.16 & .28 & \textbf{} & .47 \\
9 & PS, & Muslim & .16 & -.09 & -.13 & .06 & .05 & -.16 & .36 & .45 & \textbf{}   \\ \addlinespace \bottomrule
\end{tabularx}
\label{tab:e-1}
\end{table}
